Drawing Math

### 2022-05-09 paper/Paper.tex
main result 1

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngleJ}[2]{{\theta^{#2}_{#1}}}
\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}

@@

\begin{remark}[Polytime]
  TODO: remark about polytime
\end{remark}

@@

Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
\begin{equation}
\label{eq:wts01}  
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right)
\end{equation}
always equals $0$ or $1$ for any choice of $\beta$.

@@

We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
\begin{equation*}
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)
  \left(
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
    \right)\right)\right].
\end{equation*}
% TODO: second part can be thought of as a constant for now... ie C2=
% Then, we can think of the inner first sum as a constant of sorts, (C1)
% And we know that pI(T/T') = 1 and that pI0 = 1. So, if C1 \neq 0, we get some roots of unity
% and then the whole sum is 0...
% If it does equal 0, you have to check if C2 = 0... don't really know how to do this...
% If C1 = 0 and C2 not equal to 0, then

>>>>

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngleJ}[2]{{\theta^{#2}_{#1}}}
\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}
\newcommand{\digSumPeriodicNoJ}{\mathrm{digSumPeriodic}}
\newcommand{\totalOverRationalFrac}{\frac{\totalPeriod}{\rationalPeriodTotal}}

@@

\begin{remark}[Polytime]
  TODO: remark about discrete log and similarity... (we think this is hard, but in QPP)...
\end{remark}

@@

\newcommand{\eqWTSInnerProd}{
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right)}

Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
\begin{equation}
\label{eq:wts01}  
  \eqWTSInnerProd
\end{equation}
always equals $0$ or $1$ for any choice of $\beta$.

@@

We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
\begin{equation}
\label{eq:inner-outer-split}
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)
  \left(
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
    \right)\right)\right].
\end{equation}

\subsubsection*{Case 1}
Observe that the inner sum,
$
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
  \right)
$,
is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
let the inner sum equal $C \in \Z$.  Moreover, note that 
\begin{align*}
  &\exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)\\
  =& \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
\end{align*}
and that 
\begin{equation*}
  \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = \exp\left(0\right) = 1
\end{equation*}
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. Then, we can see that
$$
\prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = 1
$$
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$.

And so, because $\digSumPeriodic$ is a constant, we can conclude that
\begin{equation*}
 \exp\left(
      I \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right) 
\end{equation*}
is a $\totalOverRationalFrac^th$ root of unity iff $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$.

So, for $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$, we have that
\begin{align*}
  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1}
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right) \\
    &= C \sum_{p = 0}^{\totalOverRationalFrac - 1}\exp\left(W_{\totalOverRationalFrac}^p\right) \\
    &= 0.
\end{align*}
where $W_{\totalOverRationalFrac}^p$ is the $\totalOverRationalFrac^{th}$ root of unity.

If $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} = 0$, then 
\begin{align*}
  \eqWTSInnerProd &= C \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \exp(0) \\
  &= 1.
\end{align*}

So, we have now shown that \eqref{eq:wts01} is always $0$ or $1$. In particular, we also have our first 
closure result. If, $\forall \beta \in \set{0, 1}^{|A_d|}$, $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$,
\begin{align*}
  \sum_{i = 1}^T \combSingleTerm{d} &=  2^{-|A|} 
  \sum_{\beta \in \set{0,1}^{|A_d|}} 
      \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
     \exp\left(
         \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
         \seedAngle{p \rationalPeriodTotal + q}I
       \right) \\
        &= 0
\end{align*}
for all $d \in D$.
So then, $\Delta P_{0, T} = 0$ whenever 
no degree $1$ multinomials with coefficients of $-1$ or $1$ and $|A_d|$ variables has a root of $(\digSumPeriodicNoJ^1, \digSumPeriodicNoJ^2, ..., \digSumPeriodicNoJ^{|A_d|})$.
In other words, if variables, $x_1 = \digSumPeriodicNoJ^1, x_2 = \digSumPeriodicNoJ^2, ...$, there does not exist a multinomial
of form $\pm x_1 \pm x_2 \pm ... \pm x_{|A_d|} = 0$.

% TODO: second part can be thought of as a constant for now... ie C2=
% Then, we can think of the inner first sum as a constant of sorts, (C1)
% And we know that pI(T/T') = 1 and that pI0 = 1. So, if C1 \neq 0, we get some roots of unity
% and then the whole sum is 0...
% If it does equal 0, you have to check if C2 = 0... don't really know how to do this...
% If C1 = 0 and C2 not equal to 0, then
